---
title: "590 HW1"
author: "Austin Turvy Derek Holste Mason Carhart"
date: "4/13/2021"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document:
    df_print: paged
---



```{r Packages}
# Load packages
library(pacman)
p_load(readr, data.table, dplyr, janitor, haven, here, 
       tidyverse, skimr, lfe, stargazer, quantreg, hrbrthemes, 
       tinytex, kableExtra, broom)
star = stargazer(attitude, header = F)
star = sub('^.+\\caption.+$','', star)
```



```{r Data}
# Load data
af = read_dta(here("afghanistan_anonymized_data.dta")) 

```




```{r, Create nonoutlier columns}
# Create nonoutlier column
af <- af %>% mutate(nonoutlier= ifelse((f07_num_ppl_hh_cnt > 20 & f07_observed == 1) |
                                    (f07_jeribs_cnt > 10 & f07_observed == 1)|
                                    (f07_num_sheep_cnt > 50 & f07_observed == 1)|
                                      (s08_num_ppl_hh_cnt > 20 & s08_observed == 1)|
                                      (s08_jeribs_cnt > 10 & s08_observed == 1) |
                                      (s08_num_sheep_cnt > 50 & s08_observed == 1)
                                      ,0,1))


# Tabulating nonoutliers
non_outlier_tab <- af %>% group_by(nonoutlier) %>% 
    summarise(count = n(), percentage = n()/nrow(.))

non_outlier_tab
```

There are 76 non-outliers in the data given the specifications prior.

```{r table 4 column 1 regressions, echo=FALSE, results = 'asis'}

# Run girls regression for table 4 column 1
reg1 = felm(f07_formal_school ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 nonoutlier == 1 & 
                                 f07_observed == 1))

# Run boys regression for table 4 column 1
reg2 = felm(f07_formal_school ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 nonoutlier == 1 & 
                                 f07_observed == 1))

```

```{r table 4 column 1 regressions with outliers}

# Run girls regression table 4 column 1 including outliers
reg3 = felm(f07_formal_school ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 f07_observed == 1))

# Run boys regression table 4 column 1including outliers
reg4 = felm(f07_formal_school ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 f07_observed == 1))

```



```{r column 2 regressions, results = "asis"}
# Run girls regression table 4 column 1 with controls
reg5 = felm(f07_formal_school ~ treatment + chagcharan + f07_heads_child_cnt + 
              f07_age_cnt + f07_duration_village_cnt + 
              f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
              f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
              f07_jeribs_cnt + f07_num_sheep_cnt + 
              f07_nearest_scl| 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 nonoutlier == 1 &
                                 f07_observed == 1))

# Run girls regression table 4 column 1 with controls
reg6 = felm(f07_formal_school ~ treatment + chagcharan + f07_heads_child_cnt + 
              f07_age_cnt + f07_duration_village_cnt + 
              f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
              f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
              f07_jeribs_cnt + f07_num_sheep_cnt + 
              f07_nearest_scl| 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 nonoutlier == 1 &
                                 f07_observed == 1))


```
# Question 3:

```{r column 3}
# girls regression for column 3
reg7 = felm(f07_both_norma_total ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))

# boys regression for column 3
reg8 = felm(f07_both_norma_total ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))


```

# Question 4:

```{r column 4}
# girls regression column 4
reg9 = felm(f07_both_norma_total ~ treatment + chagcharan + f07_heads_child_cnt + 
              f07_age_cnt + f07_duration_village_cnt + 
              f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
              f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
              f07_jeribs_cnt + f07_num_sheep_cnt + 
              f07_nearest_scl| 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))

# boys regression column 4
reg10 = felm(f07_both_norma_total ~ treatment + chagcharan + f07_heads_child_cnt + 
              f07_age_cnt + f07_duration_village_cnt + 
              f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
              f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
              f07_jeribs_cnt + f07_num_sheep_cnt + 
              f07_nearest_scl| 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))

```

# Question 4b:

```{r column 4b}
# girls regression for column 6
reg11 = felm(s08_both_norma_total ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(s08_girls_cnt == 1 & 
                                 nonoutlier == 1 &
                                 s08_test_observed == 1))

# boys regression for column 6
reg12 = felm(s08_both_norma_total ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(s08_girls_cnt == 0 & 
                                 nonoutlier == 1 &
                                 s08_test_observed == 1))
# girls regression for column 7
reg13 = felm(s08_both_norma_total ~ treatment + chagcharan + 
               s08_heads_child_cnt + s08_age_cnt +
               s08_duration_village_cnt + s08_farsi_cnt + s08_tajik_cnt +
               s08_farmer_cnt + s08_age_head_cnt + s08_yrs_ed_head_cnt + 
               s08_num_ppl_hh_cnt + s08_jeribs_cnt + s08_num_sheep_cnt +
               s08_nearest_scl | 0 | 0 | clustercode, 
            data = af %>% filter(s08_girls_cnt == 1 & 
                                 nonoutlier == 1 &
                                 s08_test_observed == 1))

# boys regression for column 7
reg14 = felm(s08_both_norma_total ~ treatment + chagcharan + 
               s08_heads_child_cnt  + s08_age_cnt +
               s08_duration_village_cnt + s08_farsi_cnt + s08_tajik_cnt +
               s08_farmer_cnt + s08_age_head_cnt + s08_yrs_ed_head_cnt + 
               s08_num_ppl_hh_cnt + s08_jeribs_cnt + s08_num_sheep_cnt +
               s08_nearest_scl | 0 | 0 | clustercode, 
            data = af %>% filter(s08_girls_cnt == 0 & 
                                 nonoutlier == 1 &
                                 s08_test_observed == 1))

```


```{r table 2}

# Getting mean values for column 1
col_1 = af %>% 
  filter(treatment == 1 & nonoutlier == 1 & f07_observed == 1) %>% 
  select(
    c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_num_ppl_hh_cnt, f07_jeribs_cnt,  
                   f07_num_sheep_cnt, f07_nearest_scl)
  ) %>% 
  mutate(
  across(.cols = c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_num_ppl_hh_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl), mean, na.rm = TRUE)
  ) %>% head(., 1) %>% unlist(.)

# Getting mean values for column 2
col_2 = af %>% 
  filter(treatment == 0 & nonoutlier == 1 & f07_observed == 1) %>% 
  select(
    c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_num_ppl_hh_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl)
  ) %>% 
  mutate(
  across(.cols = c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_num_ppl_hh_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl), mean, na.rm = TRUE)
  ) %>% head(., 1) %>% unlist(.)



# Create regression functions for column 3
reg_function_coef = function(x){
    reg = felm(x ~ treatment | 0 | 0 | clustercode, 
               data = af %>% filter(nonoutlier == 1 & f07_observed == 1))
    coef = coef(reg)[2]
    return(coef)
}


# Regression function for SE
reg_function_se = function(x){
  reg = felm(x ~ treatment | 0 | 0 | clustercode, 
             data = af %>% filter(nonoutlier == 1 & f07_observed == 1))
  se = sqrt(diag(vcov(reg)))[2]
  return(se)
}



# Obtain column 3 coefficients
col_3_coefs = af %>% 
  filter(nonoutlier == 1 & f07_observed == 1) %>% 
  select(
    c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_num_ppl_hh_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl)
  ) %>% 
  mutate(
  across(.cols = c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_num_ppl_hh_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl), reg_function_coef)
  ) %>% head(., 1) %>% unlist(.)

# Obtain column 3 SE
col_3_se = af %>% 
  filter(nonoutlier == 1 & f07_observed == 1) %>% 
  select(
    c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_num_ppl_hh_cnt, f07_jeribs_cnt,  
                   f07_num_sheep_cnt, f07_nearest_scl)
  ) %>% 
  mutate(
  across(.cols = c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_num_ppl_hh_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl), reg_function_se)
  ) %>% head(., 1) %>% unlist(.)

# Regression for column 7
col_7 = felm(f07_formal_school ~ f07_heads_child_cnt + 
               f07_girl_cnt + f07_age_cnt + f07_duration_village_cnt + 
               f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
               f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
               f07_jeribs_cnt + f07_num_sheep_cnt + f07_nearest_scl
             | 0 | 0 | clustercode, 
             data = af %>% 
               filter(nonoutlier == 1 & f07_observed == 1 & treatment == 0))

# Regression for column 8
col_8 = felm(f07_both_norma_total ~ f07_heads_child_cnt + 
               f07_girl_cnt + f07_age_cnt + f07_duration_village_cnt + 
               f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
               f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
               f07_jeribs_cnt + f07_num_sheep_cnt + f07_nearest_scl
             | 0 | 0 | clustercode, 
             data = af %>% 
               filter(nonoutlier == 1 & f07_observed == 1 & 
                        f07_test_observed == 1 & treatment == 0))

```




```{r further analysis}

# further analysis regression
reg_fa = felm(f07_formal_school ~ f07_girl_cnt + 
         f07_nearest_scl + f07_girl_cnt*f07_nearest_scl + 
         I(f07_nearest_scl^2) | 0 | 0 | clustercode,
         data = af %>% filter(treatment==0 & 
                              f07_observed == 1 &
                              nonoutlier == 1))


```



```{r further analysis 2}

af = af %>% mutate(dist_near = if_else(f07_nearest_scl < 2, 1, 0),
               dist_close = if_else(f07_nearest_scl >= 2 & f07_nearest_scl < 3, 1, 0),
               dist_nclose = if_else(f07_nearest_scl >= 3 & f07_nearest_scl < 4, 1, 0),
               dist_far = if_else(f07_nearest_scl >= 4, 1, 0))

# Regression for near individuals
reg_near_g = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_near == 1
                              ))

# Regression for close individuals
reg_close_g = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_close == 1
                              ))

# Regression for not close individuals
reg_nclose_g = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_nclose == 1
                              ))

# Regression for far individuals
reg_far_g = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_far == 1
                              ))

# Regression for near individuals
reg_near_b= felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_near == 1
                              ))

# Regression for close individuals
reg_close_b = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_close == 1
                              ))

# Regression for not close individuals
reg_nclose_b = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_nclose == 1
                              ))

# Regression for far individuals
reg_far_b = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_far == 1
                              ))


```


```{r further analysis test}

# Regression for near individuals
reg_test_near_g = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_near == 1
                              ))

# Regression for close individuals
reg_test_close_g = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_close == 1
                              ))

# Regression for not close individuals
reg_test_nclose_g = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_nclose == 1
                              ))

# Regression for far individuals
reg_test_far_g = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_far == 1
                              ))

# Regression for near individuals
reg_test_near_b= felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_near == 1
                              ))

# Regression for close individuals
reg_test_close_b = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_close == 1
                              ))

# Regression for not close individuals
reg_test_nclose_b = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_nclose == 1
                              ))

# Regression for far individuals
reg_test_far_b = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_far == 1
                              ))

```

<div align="center">
```{r, results = "asis"}
# Table 4.1
stargazer(reg1, reg2, reg5, reg6, reg7, reg8, reg9, reg10, 
          keep.stat = c('n', 'rsq'), 
          column.labels = c("      ", "      ", "      ", "      ",
                            "      ", "      ", "      ", "      "),
          title = "Table 4: Treatment Effects by Gender",
          covariate.labels = c('Treatment', "chagcharan", 
                               "Household head's child",  "Age",
                               "Years family in village","Farsi",
                               "Tajik","Farmers","Age of household head", 
                               "Years of education of household head","Number of people in Household",
                               "Jeribs of land","Number of sheep",
                               "Distance to nearest formal school"),
          dep.var.labels = c("Formaly Enroled", "Fall Test Scores"), 
          #dep.var.labels = c(""), 
          type = 'latex', header = F, float = TRUE, 
          font.size = "small",
          column.sep.width = "-15pt",
          omit.stat=c("f", "ser"),
          notes = c("S.E Clustered by village"), notes.append = FALSE)

# Table 4b
stargazer(reg11, reg12, reg13, reg14, 
          keep.stat = c('n', 'rsq'), 
          title = "Table 4b: Treatment Effects by Gender",
          covariate.labels = c('Treatment', "chagcharan"),
          #dep.var.labels = c(""), 
          omit = c("s08_heads_child_cnt", "s08_girl_cnt", "s08_age_cnt",
                   "s08_duration_village_cnt", "s08_farsi_cnt", 
                   "s08_tajik_cnt", "s08_farmer_cnt", "s08_age_head_cnt", 
                   "s08_yrs_ed_head_cnt", "s08_num_ppl_hh_cnt", 
                   "s08_jeribs_cnt", "s08_num_sheep_cnt", "s08_nearest_scl",
                   "chagcharan"),
          type = 'latex', header = F, float = TRUE,  
          notes =c("S.E Clustered by village"), notes.append = FALSE)

# Table 2
stargazer(col_7, col_8, 
          keep.stat = c('n', 'rsq'), 
          title = "Table 2: Demographic Characteristics By Research Groups",
          covariate.labels = c("Household head's child", "Girl", 
                               "Age","Years family in village","Farsi",
                               "Tajik","Farmers","Age of household head",
                               "Years of education of household head", "Number of people in household",
                               "Jeribs of land","Number of sheep", 
                               "Distance to nearest formal school"),
          dep.var.labels = c("Formal enrollment","Test Scores"), 
          type = 'latex', header = F, float = TRUE,  
          notes =c("S.E Clustered by village"), flip = TRUE, out.header = FALSE)


col_1_df <- data.frame(name = c("Household head's child", "Girl", 
                               "Age","Years family in village","Farsi",
                               "Tajik","Farmers","Age of household head",
                               "Years of education of household head", "Number of People in Household", 
                               "Jeribs of land","Number of sheep", 
                               "Distance to nearest formal school"))
col_1_df <- col_1_df %>% mutate(Treatment_avg = c(col_1))

col_1_df <- col_1_df %>% mutate(Control_avg = c(col_2))
col_1_df <- col_1_df %>% mutate(Estimated_diff = c(col_3_coefs))
col_1_df <- col_1_df %>% mutate(Estimated_diff_se = c(col_3_se))


col_1_df %>% kbl(col.names = c("Name","Treatment Avg",
                               "Control Avg", "Estimated Diff",
                               "Estimated Difference SE"),caption = "Table 2: Demographic Characteristics By Research Groups") %>% kable_paper("hover", full_width=F)
```
</div>

<div align="center">
```{r, results = "asis"}
# Creating further analysis table for distance effects on enrollment
stargazer(reg_near_g,reg_close_g,reg_nclose_g, reg_far_g, 
          reg_near_b,reg_close_b,reg_nclose_b, reg_far_b, 
          keep.stat = c('n', 'rsq'),
          title = "Further Analysis: Distance Effect on Enrollment",
          covariate.labels = c('Treatment', "chagcharan"),
          column.labels = c("Short", "Med-Short", "Med-Long", 
                            "Long", "Short", "Med-Short", "Med-Long", "Long"),
          dep.var.labels = c("Whether or not the Individual is in a Formal School"), 
          type = 'latex', header = F, float = TRUE, 
          column.sep.width = "-10pt",
          notes =c("S.E Clustered by village 1-4 (Female), 5-8 (Male).", 
          "Both groups have increasing distance as the number increases."))

```
</div>

<div align="center">
```{r, results = "asis"}
# Creating further analysis table for distance effects on test scores
stargazer(reg_test_near_g, reg_test_close_g, reg_test_nclose_g,
          reg_test_far_g, reg_test_near_b, reg_test_close_b, 
          reg_test_nclose_b,reg_test_far_b , 
          title = "Further Analysis: Distance Effect on Test Scores",
          keep.stat = c('n', 'rsq'),
          covariate.labels = c('Treatment', "chagcharan"), 
          column.labels = c("Short", "Med-Short", "Med-Long", "Long", 
                            "Short", "Med-Short", "Med-Long", "Long"),
          dep.var.labels = c("Total Normalized Test Score, Fall 2007"), 
          type = 'latex', header = F, float = TRUE,
          column.sep.width = "-10pt",
          notes =c("S.E Clustered by village 1-4 (Female), 5-8 (Male).", 
          "Both groups have increasing distance as the number increases."))


```
</div>

```{r histrogram, message=FALSE, warning=FALSE, results='asis'}

# Creating graph for assesing distance cutoffs
ggplot(af, aes(x = f07_nearest_scl, fill = as.factor(f07_girl_cnt))) +
  geom_histogram(color = "grey", bins = 60, alpha = .9) +
  scale_fill_viridis_d(option = "C") +
  theme_minimal() +
  labs(x = "Miles From School", y = "Count", fill = "Is Girl",
       title = "Distribution of Distance from School By Gender")

```
</div>

```{r dereks reg lul, message=FALSE, warning=FALSE, results='asis'}

stargazer(reg3,reg4, out = "latex", dep.var.labels = "Formal School"
          , title = "Column 1 and 2 With Outliers", header = F)
```

\newpage

# **Written Questions:**

## Outlier question 1:
An outlier observation is someone who had more than 50 sheep or goats owned by the household in 2007 and observed in the fall of 2007 or had more than 10 jeribs of land owned by the household and was observed in the fall of 2007 or had more than 20 people in the headcount in fall of 2007 or a person that has number of people in a household greater than 20 and are observed in summer of 2008. They are also an outlier if the number of jeribs of land counted is more than 10 and are observed in summer of 2008. Lastly if the number of sheep and goats is above 50 and they are observed in summer of 2008.

## Table 4 Column 1 Question 5:
Both of our coefficient estimates were very similar as the treatment for girls and boys were exactly the same to the thousandth degree. The standard error for women was exactly the same while the standard error for men is unknown from table four.

## Table 4 Column 1 Question 6:
The coefficients on all estimates are minimuly different with the largest change being an increase in the treatment coefficient between boys of .15. For women the coefficient decreased by .11 when including outliers. The standard errors are also negligibly different. 

## Table 4 Column 2 Question 6:
Like in table 4, both treatments are statically significant. For girls, the only statistically significant control is the child's age in the fall of 2007 (5%). For The males there were more statistically significant controls. The age of the child, (1% level) if the child's family speaks Tajik, (5% level) if the head of household is a farmer or not, (10% level) and lastly the nearest schools distance, (5% level) . For both genders the child’s age was significant and positive which means that as the child grows older, they are more likely to get a better test score. 

## Further Analysis:
To start looking at the relationship at the between school we regressed formal enrolled on the distance to the nearest school, whether the child was a girl, an interaction between the two and a variables for distance squared to control for any quadratic patterns. Surprisingly the only statisally significant variable in that regression was whether or not the child was a girl. This means that being farther away does not affect formal enrollment and distance does not affect girls more than boys. The regression output does implicate that women do attend school less than their boy counterparts. Now when re-looking at formal enrollment based on four distance types, short medium short, medium long, and long, we can see that for girl, the amount of distance does not change the fact that treatment is significantly increasing enrollment or test scores. More specifically as distance increases, the effect of the treatment on tests for girls decreases while it increases for men. Meaning that the treatment is most effective for girls who live close and boys who live farther away. Interestingly the treatment for both boys and girls are mostly similar except when the schools were a medium long distance away meaning that distance does not play a significant role in how the treatment will affect the sexes. Overall it seems as though distance is a more important variable when looking at the test scores for boys and girls and not as much for their attendance rates.

