---
title: "590 HW1"
author: "Austin Turvy Derek Holste Mason Carhart"
date: "4/13/2021"
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
---



```{r Packages}
# Load packages
library(pacman)
p_load(readr, data.table, dplyr, janitor, haven, here, 
       tidyverse, skimr, lfe, stargazer, quantreg, hrbrthemes, tinytex)

```



```{r Data}
# Load data
af = read_dta(here("afghanistan_anonymized_data.dta")) 

```


1.
An outlier observation is someone who had more than 50 sheep or goats owned by the household in 2007 and in the fall of 2007 or had more than 10 jeribs of land owned by the household in the fall of 2007 or had more than 20 poeple in the houdcount in fall of 2007  or a person that has number of people in a household greater than 20 and are observed in summer of 2008. Or if number of jerribs of land counted is more than 10 and are observed in summer of 2008. Lastly if the number of sheep and goats is above 50 and they are observed in summer of 2008.

```{r, Create nonoutlier columns}
# Create nonoutlier column
af <- af %>% mutate(nonoutlier= ifelse((f07_num_ppl_hh_cnt > 20 & f07_observed == 1) |
                                    (f07_jeribs_cnt > 10 & f07_observed == 1)|
                                    (f07_num_sheep_cnt > 50 & f07_observed == 1)|
                                      (s08_num_ppl_hh_cnt > 20 & s08_observed == 1)|
                                      (s08_jeribs_cnt > 10 & s08_observed == 1) |
                                      (s08_num_sheep_cnt > 50 & s08_observed == 1)
                                      ,0,1))


# Tabulating nonoutliers
non_outlier_tab <- af %>% group_by(nonoutlier) %>% 
    summarise(count = n(), percentage = n()/nrow(.))


```


```{r}

mytable <- table(af$nonoutlier,af$nonoutlier) 
mytable 

```
There are 76 non-outliers in the data given the specifications prior.

```{r table 4 column 1 regressions, echo=FALSE, results = 'asis'}

# Run girls regression for table 4 column 1
reg1 = felm(f07_formal_school ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 nonoutlier == 1 & 
                                 f07_test_observed == 1))

# Run boys regression for table 4 column 1
reg2 = felm(f07_formal_school ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 nonoutlier == 1 & 
                                 f07_test_observed == 1))

# Create Stargazer Table
stargazer(reg1, reg2, keep.stat = c('n', 'rsq'),title = "Regression Results",
          covariate.labels = c('Treatment', "chagcharan"),
          dep.var.labels = c('Girl Enrolled in Formal School Fall 2007', 'Boy Enrolled in Formal School Fall 2007'), 
          type = 'latex', header = FALSE, float = TRUE,  notes = "S.E Clustered by village")

#Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```

```{r table 4 column 1 regressions with outliers}

# Run girls regression table 4 column 1 including outliers
reg3 = felm(f07_formal_school ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 f07_test_observed == 1))

# Run boys regression table 4 column 1including outliers
reg4 = felm(f07_formal_school ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 f07_test_observed == 1))

```



```{r column 2 regressions, results = "asis"}
# Run girls regression table 4 column 1 with controls
reg5 = felm(f07_formal_school ~ treatment + chagcharan + f07_heads_child_cnt + 
              f07_age_cnt + f07_duration_village_cnt + 
              f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
              f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
              f07_jeribs_cnt + f07_num_sheep_cnt + 
              f07_nearest_scl| 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))

# Run girls regression table 4 column 1 with controls
reg6 = felm(f07_formal_school ~ treatment + chagcharan + f07_heads_child_cnt + 
              f07_age_cnt + f07_duration_village_cnt + 
              f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
              f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
              f07_jeribs_cnt + f07_num_sheep_cnt + 
              f07_nearest_scl| 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))

# Create table with regressions with controls
stargazer(reg1, reg2, reg5, keep.stat = c('n', 'rsq'),title = "Regression Results",
          covariate.labels = c('Treatment', "chagcharan"),
          dep.var.labels = c('Girls', 'Boys', 'Girls'), 
          omit = c("f07_heads_child_cnt", "f07_girl_cnt", "f07_age_cnt", "f07_duration_village_cnt", "f07_farsi_cnt", "f07_tajik_cnt", "f07_farmer_cnt", "f07_age_head_cnt", "f07_yrs_ed_head_cnt", "f07_num_ppl_hh_cnt", "f07_jeribs_cnt", "f07_num_sheep_cnt", "f07_nearest_scl"),
          type = 'latex', header = FALSE, float = TRUE,  notes = "S.E Clustered by village")

```
# Question 3:

```{r column 3}
# girls regression for column 3
reg7 = felm(f07_both_norma_total ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))

# boys regression for column 3
reg8 = felm(f07_both_norma_total ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))


```

# Question 4:

```{r column 4}
# girls regression column 4
reg9 = felm(f07_both_norma_total ~ treatment + chagcharan + f07_heads_child_cnt + 
              f07_age_cnt + f07_duration_village_cnt + 
              f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
              f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
              f07_jeribs_cnt + f07_num_sheep_cnt + 
              f07_nearest_scl| 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 1 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))

# boys regression column 4
reg10 = felm(f07_both_norma_total ~ treatment + chagcharan + f07_heads_child_cnt + 
              f07_age_cnt + f07_duration_village_cnt + 
              f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
              f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
              f07_jeribs_cnt + f07_num_sheep_cnt + 
              f07_nearest_scl| 0 | 0 | clustercode, 
            data = af %>% filter(f07_girl_cnt == 0 & 
                                 nonoutlier == 1 &
                                 f07_test_observed == 1))

```

# Question 4b:

```{r column 4b}
# girls regression for column 6
reg11 = felm(s08_both_norma_total ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(s08_girls_cnt == 1 & 
                                 nonoutlier == 1 &
                                 s08_test_observed == 1))

# boys regression for column 6
reg12 = felm(s08_both_norma_total ~ treatment + chagcharan | 0 | 0 | clustercode, 
            data = af %>% filter(s08_girls_cnt == 0 & 
                                 nonoutlier == 1 &
                                 s08_test_observed == 1))
# girls regression for column 7
reg13 = felm(s08_both_norma_total ~ treatment + chagcharan + 
               s08_heads_child_cnt + s08_age_cnt +
               s08_duration_village_cnt + s08_farsi_cnt + s08_tajik_cnt +
               s08_farmer_cnt + s08_age_head_cnt + s08_yrs_ed_head_cnt + 
               s08_num_ppl_hh_cnt + s08_jeribs_cnt + s08_num_sheep_cnt +
               s08_nearest_scl | 0 | 0 | clustercode, 
            data = af %>% filter(s08_girls_cnt == 1 & 
                                 nonoutlier == 1 &
                                 s08_test_observed == 1))

# boys regression for column 7
reg14 = felm(s08_both_norma_total ~ treatment + chagcharan + 
               s08_heads_child_cnt  + s08_age_cnt +
               s08_duration_village_cnt + s08_farsi_cnt + s08_tajik_cnt +
               s08_farmer_cnt + s08_age_head_cnt + s08_yrs_ed_head_cnt + 
               s08_num_ppl_hh_cnt + s08_jeribs_cnt + s08_num_sheep_cnt +
               s08_nearest_scl | 0 | 0 | clustercode, 
            data = af %>% filter(s08_girls_cnt == 0 & 
                                 nonoutlier == 1 &
                                 s08_test_observed == 1))

```


```{r table 2}

# Getting mean values for column 1
col_1 = af %>% 
  filter(treatment == 1 & nonoutlier == 1 & f07_observed == 1) %>% 
  select(
    c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl)
  ) %>% 
  mutate(
  across(.cols = c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl), mean, na.rm = TRUE)
  ) %>% head(., 1) %>% unlist(.)

# Getting mean values for column 2
col_2 = af %>% 
  filter(treatment == 0 & nonoutlier == 1 & f07_observed == 1) %>% 
  select(
    c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl)
  ) %>% 
  mutate(
  across(.cols = c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl), mean, na.rm = TRUE)
  ) %>% head(., 1) %>% unlist(.)



# Create regression functions for column 3
reg_function_coef = function(x){
    reg = felm(x ~ treatment | 0 | 0 | clustercode, 
               data = af %>% filter(nonoutlier == 1 & f07_observed == 1))
    coef = coef(reg)[2]
    return(coef)
}


# Regression function for SE
reg_function_se = function(x){
  reg = felm(x ~ treatment | 0 | 0 | clustercode, 
             data = af %>% filter(nonoutlier == 1 & f07_observed == 1))
  se = sqrt(diag(vcov(reg)))[2]
  return(se)
}



# Obtain column 3 coefficients
col_3_coefs = af %>% 
  filter(nonoutlier == 1 & f07_observed == 1) %>% 
  select(
    c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl)
  ) %>% 
  mutate(
  across(.cols = c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl), reg_function_coef)
  ) %>% head(., 1) %>% unlist(.)

# Obtain column 3 SE
col_3_se = af %>% 
  filter(nonoutlier == 1 & f07_observed == 1) %>% 
  select(
    c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl)
  ) %>% 
  mutate(
  across(.cols = c(f07_heads_child_cnt, f07_girl_cnt, f07_age_cnt, f07_duration_village_cnt,
                   f07_farsi_cnt,  f07_tajik_cnt,  f07_farmer_cnt, 
                   f07_age_head_cnt, f07_yrs_ed_head_cnt, f07_jeribs_cnt, 
                   f07_num_sheep_cnt, f07_nearest_scl), reg_function_se)
  ) %>% head(., 1) %>% unlist(.)

# Regression for column 7
col_7 = felm(f07_formal_school ~ f07_heads_child_cnt + 
               f07_girl_cnt + f07_age_cnt + f07_duration_village_cnt + 
               f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
               f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
               f07_jeribs_cnt + f07_num_sheep_cnt + f07_nearest_scl
             | 0 | 0 | clustercode, 
             data = af %>% 
               filter(nonoutlier == 1 & f07_observed == 1 & treatment == 0))

# Regression for column 8
col_8 = felm(f07_both_norma_total ~ f07_heads_child_cnt + 
               f07_girl_cnt + f07_age_cnt + f07_duration_village_cnt + 
               f07_farsi_cnt + f07_tajik_cnt + f07_farmer_cnt + 
               f07_age_head_cnt + f07_yrs_ed_head_cnt + f07_num_ppl_hh_cnt + 
               f07_jeribs_cnt + f07_num_sheep_cnt + f07_nearest_scl
             | 0 | 0 | clustercode, 
             data = af %>% 
               filter(nonoutlier == 1 & f07_observed == 1 & 
                        f07_test_observed == 1 & treatment == 0))

```


```{r, results = "asis"}
stargazer(col_1,col_2,col_3_coefs,col_3_se,col_7,col_8, keep.stat = c('n', 'rsq'),title = "Regression Results",
          covariate.labels = c(NULL), column.labels = c(NULL),
          dep.var.labels = c(NULL), 
          type = 'latex', header = F, float = TRUE,  notes =c( "S.E Clustered by village"))


```



```{r further analysis}

# further analysis regression
reg_fa = felm(f07_formal_school ~ f07_girl_cnt + 
         f07_nearest_scl + f07_girl_cnt*f07_nearest_scl + 
         I(f07_nearest_scl^2) | 0 | 0 | clustercode,
         data = af %>% filter(treatment==0 & 
                              f07_observed == 1 &
                              nonoutlier == 1))


```

```{r histrogram}


#ggplot(af, aes(x = f07_nearest_scl, fill = as.factor(f07_girl_cnt))) +
#  geom_histogram(color = "grey", bins = 60, alpha = .9) +
#  scale_fill_viridis_d(option = "C") +
#  theme_modern_rc(ticks = TRUE, plot_title_size = 13) +
#  labs(x = "Miles From School", y = "Count", fill = "Is Girl", 
#       title = "Distribution of Distance from School By Gender")

```


```{r further analysis 2}

af = af %>% mutate(dist_near = if_else(f07_nearest_scl < 2, 1, 0),
               dist_close = if_else(f07_nearest_scl >= 2 & f07_nearest_scl < 3, 1, 0),
               dist_nclose = if_else(f07_nearest_scl >= 3 & f07_nearest_scl < 4, 1, 0),
               dist_far = if_else(f07_nearest_scl >= 4, 1, 0))

# Regression for near individuals
reg_near_g = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_near == 1
                              ))

# Regression for close individuals
reg_close_g = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_close == 1
                              ))

# Regression for not close individuals
reg_nclose_g = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_nclose == 1
                              ))

# Regression for far individuals
reg_far_g = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_far == 1
                              ))

# Regression for near individuals
reg_near_b= felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_near == 1
                              ))

# Regression for close individuals
reg_close_b = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_close == 1
                              ))

# Regression for not close individuals
reg_nclose_b = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_nclose == 1
                              ))

# Regression for far individuals
reg_far_b = felm(f07_formal_school ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_far == 1
                              ))


```


```{r further analysis test}

# Regression for near individuals
reg_test_near_g = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_near == 1
                              ))

# Regression for close individuals
reg_test_close_g = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_close == 1
                              ))

# Regression for not close individuals
reg_test_nclose_g = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_nclose == 1
                              ))

# Regression for far individuals
reg_test_far_g = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 1 &
                              dist_far == 1
                              ))

# Regression for near individuals
reg_test_near_b= felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_near == 1
                              ))

# Regression for close individuals
reg_test_close_b = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_close == 1
                              ))

# Regression for not close individuals
reg_test_nclose_b = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_nclose == 1
                              ))

# Regression for far individuals
reg_test_far_b = felm(f07_both_norma_total ~ treatment + 
                   chagcharan | 0 | 0 | clustercode,
         data = af %>% filter( 
                              f07_observed == 1 &
                              nonoutlier == 1 &
                              f07_girl_cnt == 0 &
                              dist_far == 1
                              ))

```




```{r, results = "asis"}

stargazer(reg_near_g,reg_close_g,reg_nclose_g, reg_far_g, reg_near_b,reg_close_b,reg_nclose_b, reg_far_b, keep.stat = c('n', 'rsq'),title = "Regression Results",
          covariate.labels = c('Treatment', "chagcharan"), column.labels = c("Short", "Med-Short", "Med-Long", "Long", "Short", "Med-Short", "Med-Long", "Long"),
          dep.var.labels = c("Whether or not the Individual is in a Formal School"), 
          type = 'latex', header = F, float = TRUE,  notes =c( "S.E Clustered by village 1-4 (Female), 5-8 (Male).", 
          "Both groups have increasing distance as the number increases."))

```


```{r, results = "asis"}

stargazer(reg_test_near_g, reg_test_close_g, reg_test_nclose_g,reg_test_far_g, reg_test_near_b, reg_test_close_b, reg_test_nclose_b,reg_test_far_b , keep.stat = c('n', 'rsq'),title = "Regression Results",
          covariate.labels = c('Treatment', "chagcharan"), column.labels = c("Short", "Med-Short", "Med-Long", "Long", "Short", "Med-Short", "Med-Long", "Long"),
          dep.var.labels = c("Total Normalized Test Score, Fall 2007"), 
          type = 'latex', header = F, float = TRUE,  notes =c( "S.E Clustered by village 1-4 (Female), 5-8 (Male).", 
          "Both groups have increasing distance as the number increases."))

```



